Under-approximation of reachability in multivalued asynchronous networks

### 2013-04-02 parts/appendix.tex
title in appendix
weak bisimulation of DNs
section 3
proofreading of section 3
several fixes; first final version

%\section{Demonstration of \pref{th:approxinf}}

\begin{proof} \towrite{Déplacer en annexe}
We note $max\ctx = \ctx \Cap \allprocs(\cwB)$ the context supported by $\cwB$.

@@

\section{Demonstration of \towrite{équivalence PHP / réseaux discrets}}

\todo{Preuve}

>>>>

\section{Proof of Under-approximation (\pref{th:approxinf})}
\label{suppl:demoapproxinf}

In the following, we denote:
%$\BvProc = \Bv \cap \PHproc$, $\BvObj = \Bv \cap \Obj$ and $\BvSol = \Bv \cap \Sol$.
$\Bee{X}{Y} = \Be \cap (X \times Y)$, with $X, Y$ amongst $\PHproc$, $\Obj$ and $\Sol$.

\begin{proof}
We note $max\ctx = \ctx \Cap \allprocs(\cwB)$ the context supported by $\cwB$.

@@

\input{parts/suppl-ph-dn.tex}

### 2013-04-02 parts/ccl.tex
several fixes; first final version

We introduced a new semantics to include priorities into the Process Hitting framework, which prove especially useful to model cooperations.
Then, we developed a method to efficiently perform a reachability analysis of a sequence of objectives in a restricted class of Process Hitting models,
but it is also useful to establish the reachability of a partial state.
This analysis is based on an under-approximation of the true reachability solutions.
%; however, the most usual cases can be handled.
The method has been implemented as an extension of the existing “ph-reach” tool into the existing Pint\footnote{\url{http://processhitting.wordpress.com/}} library.
\towrite{Déplacer dans la section exemples ?}

We showed that the class of Process Hitting models that can be handled by the aforementioned method are equivalent to Asynchronous Discrete Networks, and therefore to Asynchronous Boolean Networks.
This allows to efficiently compute reachability results on large biological models provided that they are equivalent to Asynchronous Discrete Networks and that a translation from the original framework into a Process Hitting model is possible.
Such a translation for interaction graphs of Thomas modelling was proposed in~\cite{PMR10-TCSB} \towrite{[À garder ?] and is made possible by the Pint software}.

>>>>

We introduced a new semantics to include priorities into the Process Hitting framework, which prove especially useful to model cooperations.
Then, we developed a method to efficiently perform a reachability analysis of a sequence of objectives in a restricted class of Process Hitting models,
but it is also useful to establish the reachability of a partial state.
This analysis is based on an under-approximation of the true reachability solutions.
%; however, the most usual cases can be handled.

We showed that the class of Process Hitting models that can be handled by the aforementioned method are equivalent to Asynchronous Discrete Networks, and therefore to Asynchronous Boolean Networks.
This allows to efficiently compute reachability results on large biological models provided that they are equivalent to Asynchronous Discrete Networks and that a translation from the original framework into a Process Hitting model is possible.
Such a translation for interaction graphs of Thomas modelling was proposed in~\cite{PMR10-TCSB}. % \towrite{[À garder ?] and is made possible by the Pint software}.
